### 2017-12-22 paper/jfp-submission/related.tex
related work

A function's type is a theorem about its behavior.
Thus, \toolname's witnesses can be viewed as \emph{counter-examples},
thereby connecting it to work on using test cases to find
counter-examples prior to starting a proof~\cite{ACL2Testing, Seidel15}.

@@

Flanagan~\etal~\shortcite{Flanagan96} describe a static debugger for Scheme, which helps
the programmer interactively visualize problematic source-sink flows
corresponding to soft-typing errors. The debugger allows the user to explore
an abstract reduction graph computed from a static value set analysis of
the program. In contrast, \toolname generates witnesses and allows the user
to explore the resulting dynamic execution.
%
Perera~\etal~\shortcite{Perera2012-dy} present a tracing semantics
for functional programs that tags values with their provenance, enabling
a form of backwards program slicing from a final value to the sequence
of reductions that produced it. Notably, they allow the user to supply a
\emph{partial value} --- containing holes --- and present a partial slice,
containing only those steps that affected the the partial value.
% This
% system is designed to answer questions of the form ``Where did this
% value come from?'' and thus is focused on backward exploration.
Perera~\etal\ focus on backward exploration; in contrast, our
visualization supports forward \emph{and} backward exploration, though
our backward steps are more limited.
%
Specifically, we do not support selecting a value and inserting the
intermediate terms that preceded it while ignoring unrelated computation
steps. %; this would be interesting future work.

>>>>

A function's type is a theorem about its behavior.
Thus, \toolname's witnesses can be viewed as \emph{counter-examples},
thereby connecting it to work on using test cases to find
counter-examples prior to starting a proof~\cite{ACL2Testing, Nguyen2015-oo, Seidel15}.

@@

Flanagan~\etal~\shortcite{Flanagan96} describe a static debugger for Scheme, which helps
the programmer interactively visualize problematic source-sink flows
corresponding to soft-typing errors. The debugger allows the user to explore
an abstract reduction graph computed from a static value set analysis of
the program. In contrast, \toolname generates witnesses and allows the user
to explore the resulting dynamic execution.

Clements~\etal~\shortcite{Clements2001-qj} present a reduction-based
visualization of program execution similar to \toolname's, though their
interaction model is closer to that of a traditional step-debugger,
limited to taking single step forwards or backwards. In contrast,
\toolname first presents an overview of the whole computation, and then
allows the user to focus in on the interesting reductions.

Perera~\etal~\shortcite{Perera2012-dy} present a tracing semantics
for functional programs that tags values with their provenance, enabling
a form of backwards program slicing from a final value to the sequence
of reductions that produced it. Notably, they allow the user to supply a
\emph{partial value} --- containing holes --- and present a partial slice,
containing only those steps that affected the the partial value.
% This
% system is designed to answer questions of the form ``Where did this
% value come from?'' and thus is focused on backward exploration.
Perera~\etal\ focus on backward exploration; in contrast, our
visualization supports forward \emph{and} backward exploration, though
our backward steps are more limited.
%
Specifically, we do not support selecting a value and inserting the
intermediate terms that preceded it while ignoring unrelated computation
steps. %; this would be interesting future work.
